### 2014-06-19 Equipment/Equipment_Guide/Equipment_Guide.tex
Water Flow Sensor: Update Arduino sketch name

\begin{enumerate}
\item Install Arduino IDE
http://arduino.cc/
\item Plug the Arduino Yun into the USB port of the host computer.
\item Set the Tools > Board to Arduino Yun and the Tools > Port to the /dev/ttyusbmodemXXXXXX setting that matches the plugged-in Arduino.
\item A Sketch is a script that runs on the Arduino microcontroller. Using the Arduino IDE, install the pressure\_sensor Sketch on the Arduino from the NIST-FIRE repository. This enables the reading and writing of data from the analog-to-digital converter via the REST API on the Arduino. Note: this sketch requires the Adafruit ADS 1015 library from https://github.com/adafruit/Adafruit\_ADS1X15.
\end{enumerate}

>>>>

\begin{enumerate}
\item Install Arduino IDE
http://arduino.cc/
\item Plug the Arduino Yun into the USB port of the host computer.
\item Set the Tools > Board to Arduino Yun and the Tools > Port to the /dev/ttyusbmodemXXXXXX setting that matches the plugged-in Arduino.
\item A Sketch is a script that runs on the Arduino microcontroller. Using the Arduino IDE, install the adc\_voltage Sketch on the Arduino from the NIST-FIRE repository. This enables the reading and writing of data from the analog-to-digital converter via the REST API on the Arduino. Note: this sketch requires the Adafruit ADS 1X15 library from https://github.com/adafruit/Adafruit\_ADS1X15.
\end{enumerate}
